Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-07-14 paper.tex
djfkdjf

An alternative to these two traditional single-notch searches is a limited multi-notch search that allows mass differences between precursor and theoretical peptide of 0, 1.0029 or 2.0054 Da but limits the width about any one of those three tolerances to a few ppm (1-20 ppm).
This approach provides a means of getting an increased number of correct identifications but mitigates problems with wrong identifications.
This alternative would appear to result in loss of identification of co-isolated peptides, but MetaMorpheus is programmed to mitigate this problem by identifying multiple co-isolated precursor masses, see below.

To qualitatively illustrate the described advantages, we conducted the three searches on all 28 calibrated Jurkat fractions.
The numbers of confidently identified PSMs, misassigned PSMs are reported in Table~\ref{tbl:singleVsMultiNotch}.

>>>>

An alternative to these two traditional single-notch searches is a limited multi-notch search that allows mass differences between precursor and theoretical peptide of 0, 1.0029 or 2.0054 Da but limits the width about any one of those three tolerances to a few ppm (1-20 ppm).
This approach provides a means of getting an increased number of correct identifications but mitigates problems with wrong identifications.
This alternative would appear to result in loss of identification of co-isolated peptides, but MetaMorpheus is programmed to mitigate this problem by identifying multiple co-isolated precursor masses, see section below.

To qualitatively illustrate the described advantages, we conducted the three searches on all 28 calibrated Jurkat fractions.
The numbers of confidently identified PSMs and misassigned PSMs are reported in Table~\ref{tbl:singleVsMultiNotch}.
